Pretty darn good control: when are approximate solutions better than approximate models

### 2023-06-22 manuscript/manuscript.Rmd
included timeseries figure

The sensitivity of the policy to, e.g., the values of $Z$ can be seen in the sample time series displayed in Fig. **TBD**.
Here, we can see that species $Z$ becomes endangered due to harvesting for all management strategies.
The DRL-based strategy, however, is sensitive to the values of $Z$ and can respond accordingly by scaling the fishing effort with the value of $Z$.
In particular, the policy responds to periods of low values of $Z$ by restricting fishing on $X$ and $Y$, thus promoting $Z$'s growth.
This pattern is rather common among the whole dataset---early episode ends are largely due to near-extinctions of $Z$ for all management strategies.

>>>>

This sensitivity of the policy to, for instance, the values of $Z$ can be seen in the sample time series displayed in Fig. \ref{fig:gpp-ep}.
Here, we can see that species $Z$ becomes endangered due to harvesting for all management strategies.
The DRL-based strategy, however, is sensitive to the values of $Z$ and can respond accordingly by scaling the fishing effort with the value of $Z$.
In particular, the policy responds to the period of diminishing values of $Z$ near the end of the episode, by restricting fishing on $X$ and $Y$, thus promoting $Z$'s growth.
This pattern is rather common among the whole dataset---early episode ends are largely due to near-extinctions of $Z$ for all management strategies.

\begin{figure}
  \centering
  \includegraphics[scale=0.33]{figures/timeseries-gpp.jpeg}
  \caption{Time-series of an episode managed with $\pi_{\text{PPO+GP}}$. Here we plot the state of the system on the bottom panel, and the actions taken (fishing efforts on $X$ and $Y$---respectively $M_X$ and $M_Y$) on the top panel.}
  \label{fig:gpp-ep}
\end{figure}
